Parallelizing Linear Recurrent Neural Nets Over Sequence Length

### 2018-04-22 poster/main.tex
Add GILR-LSTM description

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\begin{block}{Background}

Large minibatches are necessary for computational performance but create large memory
requirements and may damage model generalization ability.

@@

Given $x_t$, $\lambda_t$ can compute $h_t=\lambda_t h_{t-1} + x_t$ for $t=1\ldots T$ on $p$
processors in $O(T/p + \log(p))$ with the classic parallel scan algorithm.

This statement requires citation \cite{Smith:2012qr}.

@@

\begin{block}{Materials}

The following materials were required to complete the research:

\begin{itemize}
\item Curabitur pellentesque dignissim
\item Eu facilisis est tempus quis
\item Duis porta consequat lorem
\item Eu facilisis est tempus quis
\end{itemize}

The materials were prepared according to the steps outlined below:

\begin{enumerate}
\item Curabitur pellentesque dignissim
\item Eu facilisis est tempus quis
\item Duis porta consequat lorem
\item Curabitur pellentesque dignissim
\end{enumerate}

@@

\begin{block}{Methods}

@@

\begin{alertblock}{Important Result}

>>>>

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------
\begin{block}{Background}
Large minibatches are necessary for computational performance but create large memory
requirements and may damage model generalization ability.

@@

Given $x_t$, $\lambda_t$ can compute $h_t=\lambda_t h_{t-1} + x_t$ for $t=1\ldots T$ on $p$
processors in $O(T/p + \log(p))$ with the classic parallel scan algorithm.
\end{block}

\begin{block}{Gated Impulse Linear Recurrence}
We designed a recurrent layer that can take maximium advantage of parallel linear recurrence??

\begin{align*}
g_t &= \sigma(Ux_t + b_g) \\
i_t &= \tau(Vx_t + b_z) \\
h_t &= g_t \odot h_{t-1} + (1-g_t)\odot i_t
\end{align*}
\end{block}

@@

\begin{block}{Linear Surrogate RNNs}

RNNs have a transition function $s_t = f(s_{t-1},x_t)$. $s_t$ serves dual roles as a
summary of the past as well as the output of the unit. Non-linear $f$ in units such
as vanilla RNN and LSTM prevents parallelization over sequence length.

Replacing the summary of the past $s_{t-1}$ with a linear surrogate $\tilde{s}_{t-1}$
allows the easy adaption of any existing RNN architecture for parallel computation.

The state of an LSTM consists of $(c_t, h_t)$. $c_t$ is already computed
by linear recurrence, so a linear surrogate LSTM must only compute a
linear $\tilde{h}_t$. We let $h = \text{GILR}(x)$ and call it a GILR-LSTM.

@@

\begin{block}{Scan diagram and complexity??}

@@

\begin{alertblock}{Important Result (???)}
